State of the Practice of Lattice Boltzmann Method Software Development

### 2021-06-25 StateOfPractice/Peter-Notes/Report/Report.tex
updated chapter 5 LBM report

>>>>

Table \ref{rankingcomparison} compares the top 10 ranked LBM software packages with a LBM package ranking made by a domain expert. Five (Palabos, OpenLB, LUMA, waLBerla, Sailfish) of the top 10 ranked packages in this assessment are also found in the domain expert's list. Interestingly, these five packages are listed in the same order on both lists. Looking at the remaining packages, the top two ranked packages in this state of the practice assessment (Ludwig, ESPResSo) are not on the domain expert's list. Perhaps the intended applications of these packages, complex fluids for Ludwig and soft matter research for ESPResSo, do not align with the research interests of the domain expert, and this is why they did not make it onto their list. Moving down the list, pyLBM and DL\_MESO(LBE) did not make the domain expert's top 10 list but were mentioned by the domain expert. The 10th ranked package, laboetie, was not mentioned by the domain expert. Looking at the remainder of the domain expert's list, ASL is a general purpose tool for solving partial differential equations and may have fallen out of scope of the authoritative lists that were used to identify the initial LBM software list. The domain expert's fifth ranked package (ch4-project) was on the initial software list of this assessment, but was removed due to a lack of documentation. Open FSI is a new project that uses Palabos. It was made public the year before data was collected for this state of the practice exercise. It may not have been on authoritative lists due to its age. Similarly, LIFE was also made public recently. Finally, the domain expert's 10th ranked package (HemeLB) was ranked 20th in this state of the practice assessment.

\begin{center}
	\begin{onehalfspacing}
		\begin{tabular}{ p{2cm}p{3.5cm}p{3.5cm}}
			\hline
			Rank & This Assessment & Domain Expert\\
			\hline
			1&Ludwig&Palabos\\
			2&ESPResSo &OpenLB\\
			3&Palabos &LUMA\\
			4&OpenLB &ASL\\
			5&LUMA&ch4-project\\
			6&pyLBM &Open FSI\\
			7&DL\_MESO (LBE) & WaLBerla\\
			8&waLBerla & LIFE\\
			9&Sailfish &Sailfish\\
			10&laboetie &HemeLB\\		
			\hline
		\end{tabular}
		\captionof{table}{Ranking Comparison}\label{rankingcomparison}
	\end{onehalfspacing}
\end{center}
